Title

### 2021-09-01 paper/main.tex
Different expression for the free energy

Where $k_B$ is Boltzmann's constant and T is the
temperature. Replacing Eq.~(\ref{eq:A-from-p}) in
Eq.~(\ref{eq:Adsorption}) we can relate the free energy of adsorption
to the probabilities of the near and free states:

@@

If the potential PMF along $\xi$ has been estimated for the discrete
states $\{\xi_1, \xi_2, ..., \xi_N \}$, the probability of a state
$\xi_{j}$ can be estimated with:

@@

On the following sections, two different methods used to obtain a PMF along $\xi$ will be described.

>>>>

Where $k_B$ is Boltzmann's constant and T is the
temperature. Replacing Eq.~(\ref{eq:A-from-p}) in
Eq.~(\ref{eq:Adsorption}) we get an expression to calculate the free
energy of adsorption from the probabilities of the near and free
states:

@@

If the PMF along $\xi$ has been estimated for the discrete
states $\{\xi_1, \xi_2, ..., \xi_N \}$, the probability of a state
$\xi_{j}$ can be estimated with:

@@

or, equivalently:

\begin{equation}
\label{eq:Aads-from-PMF-p}
\Delta A^{ads} = - k_B T \ln \left(\frac{\sum_{j \in near} p_{\xi_j}}{\sum_{k \in free} p_{\xi_k}}\right)
\end{equation}
On the following sections, two different methods used to obtain a PMF along $\xi$ will be described.
